Checkpoint 4

### 2020-05-03 Draft-Report.Rmd
Update Draft-Report.Rmd

##Repeated Measures + Normal Regression (WILL) (1|State)**

@@

###Complex Model

@@

###Complex Model 
```{r}
set.seed(454)
pred_complex <- posterior_predict(
  complexmod,
  newdata = Finaldata, transform = TRUE)

>>>>

## Repeated Measures + Normal Regression (WILL) (1|State)**

@@

### Complex Model

@@

### Complex Model 
```{r}
set.seed(454)
pred_complex <- posterior_predict(
  complexmod,
  newdata = Finaldata, transform = TRUE)
